User-level Grid Monitoring with Inca 2

### 2007-02-28 pubs/papers/hpdc-gmw-2007/paper.tex
reformatted intro bullets to start with verb and removed use of "guidelines" in following text -- Kate, can you make a pass on these updates (specifically, the 5th and 7th bullets)
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6602 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

% Standard "Grids are good" intro paragraph.  But are complex.  
Grid systems provide unified and coherent access to distributed computing,
data storage and analysis, instruments, and other resources.  These systems
require the careful coordination of software packages, services, and
configurations across multiple, heterogeneous resources.  The TeraGrid
project~\cite{teragrid}, for example, manages the coordination of software and
services by deploying and monitoring a common user environment across
distributed, heterogeneous resources. The organization of TeraGrid software
and services is referred to as the Coordinated TeraGrid Software and Services
(CTSS).  TeraGrid's software and services uniformity simplifies access to its
resources, which consist of more than 102 teraflops of compute capability and
more than 15 petabytes of online storage, all interconnected by a network that
can transfer a terabyte of data in under 10 minutes.

% Complex means they are difficult to provide and maintain. Describe the
% stakeholders.   Monitoring is needed.
Providing and maintaining a stable infrastructure for these complex 
Grid systems poses challenges for both administrators who build and
maintain Grid resources and scientists who use them.  First, system
administration is distributed across multiple administrative domains 
requiring a significant amount of coordination.  This is typically performed by
a group of Grid administrators or operators who consider local site policies and
resource heterogeneity
and decide when software (including updates and patches) should be deployed to
resources and how it should be configured.  
Each site's system administrators, who are not necessarily Grid
experts, are then responsible for providing the required Grid software
components and services for their resource and debugging any problems that
arise.  Well-defined requirements and good communication are required in this
model.  Otherwise, inconsistencies between the resources arise that either
inconvenience the user or prevent them from using a particular resource
altogether.  A second challenge is that failures will occur over
time in the Grid services due to network or system failures, software
misconfiguration, or software bugs.  In order to address these challenges,
Grid monitoring can be used to detect such problems, leading to a more
stable and dependable Grid infrastructure.

@@

% What user-level monitoring provides and why we think it is good
User-level Grid monitoring is Grid infrastructure testing and performance measurement 
from a generic, impartial user's perspective.  The goal of user-level monitoring is 
to detect and fix Grid infrastructure problems before users notice them -- 
user complaints should not be the first indication of Grid failures.  
In our view, the following guidelines define user-level Grid monitoring:

@@

\item In order to reflect regular user experiences, tests or performance
measurements of the Grid infrastructure should be done from a standard user
account.  It is important not to execute from a system administrator's account,
since it may have special privileges and use custom shell initialization files.

\item Also in order to reflect regular user experiences, tests should be
written and configured using information directly from user documentation
(e.g., hostnames, ports, pathnames, etc.).  This may not always be possible
when documentation and testing are done in parallel in a pre-production
environment, but they should be closely coordinated activities.

\item Since Grids are dynamic, user-level tests or performance measurements
should be automated and executed periodically.

\item User-level tests and performance measurements should be written and
maintained within an iterative refinement process.  An iterative process is
required since Grids are dynamic and software environments change over time as
packages are upgraded.  It is also difficult to write and deploy a test
correctly the first time because of portability issues and incomplete user
documentation.  For example, it may take some iterations to determine whether a
detected failure is the result of a faulty test, user document, or Grid
resource.

\item In order to determine overall Grid health, monitoring must be flexible
enough to include many types of user-level tests and performance measurements.
Typically all of the commands listed in the user documentation and/or at least
one basic test for each software component of the Grid infrastructure is
required.

\item Tests or performance measurements that interact with Grid services
require authentication and should be executed using a standard user GSI
credential that is mapped to the standard user account.

\item Tests or performance measurements should be executed locally on all Grid
resources when appropriate so that all Grid access points available to users
are verified.  Similarly, it is important to execute some tests all-to-all
in order to detect site-to-site configuration errors such as authentication
problems.

\item The configuration of tests or performance measurements should be managed
centrally in order to ensure consistent testing of the resources, rather than
by system administrators who may not use the same information that is
available to users.

@@

\noindent In 2003 SDSC, in partnership with TeraGrid, began developing Inca
1~\cite{inca1} to implement a user-level Grid monitoring system with the above
features and started using it to
verify that CTSS was deployed consistently across all TeraGrid resources and
to monitor its status.  At that time, the only available user-level Grid
monitoring tools were the NCSA TestGrid script~\cite{ncsa-test} and
Grid Integration Test Script~\cite{gits}, both of which ran a fixed number of Grid tests and formatted
results in HTML.  Although these tools were easy to install and produced
useful information, they showed the view of the Grid from a single
resource, lacked automation, and were not easily extensible.

The initial
version of Inca was implemented as a client-server architecture.  It provided
data collection, data storage (accessible from a Web services interface and with 
limited archiving capabilities), and data display though Web status
pages.  Inca 1 was first deployed to TeraGrid in mid 2003 and released in late
2003. After running Inca 1 for a year and a half on TeraGrid, we learned some
valuable lessons and designed Inca 2, our current release.  Inca 2
contains a number of substantial improvements over Inca 1 with respect to
security, installation and maintenance, and storage capabilities.  Inca 2 has
been running on TeraGrid since November 2006, and in February 2007 a production
version of the software was released.  Currently, seven other Grids in the
U.S., Europe, and Australia use Inca.

@@

% Implements user-level Grid monitoring and who it benefits
Inca 2 is a system that provides user-level monitoring of Grid functionality
and performance.  It was designed to be
general, flexible, scalable, and secure, in addition to being easy to deploy
and maintain.  Inca benefits Grid operators who oversee the day-to-day
operation of a Grid; system administrators who provide and manage resources;
and users who run applications on a Grid.  Besides meeting the guidelines 
described in Section~\ref{intro}, Inca 2 has additional features
listed below.  A '*' after the feature description indicates it is a new
feature of Inca 2; other items note improvements to Inca 1 features.  The 
Inca system:

@@

\begin{figure*}[tbp]
  \centering
  \mbox{\epsfig{file=arch.eps, width=.7\textwidth}}
  \caption{\label{arch_fig} Inca architecture.}
\end{figure*}

% overview description of components
Figure~\ref{arch_fig} shows the architecture of Inca 2.
Inca 2 is composed of 3 core
components (in highlighted box):  the agent, depot, and reporter manager.
The \textit{agent} and \textit{reporter managers} coordinate the execution of
tests and performance measurements on the Grid resources and the
\textit{depot} stores and archives the results.  The inputs to Inca 2 are one
or more \textit{reporter repositories} that contain user-level tests and
benchmarks, called \textit{reporters}, and a configuration file describing how
to execute them on the Grid resources.  This configuration is normally created
using an administration GUI tool
called \textit{incat} (Inca Administration Tool).  The output or results
collected from the resources are queried by the \textit{data consumer} and
displayed to users.  The following steps describe how an Inca administrator
would deploy user-level tests and/or performance measurements to their
resources.

@@

\item Using the guidelines described in the introduction, the Inca
administrator either writes reporters to monitor their Grid or uses existing
reporters in a published repository.

@@

An Inca reporter is an executable program that tests or measures some aspect
of a system or installed software.   Reporter executables are designed to be
easy to produce and can be run outside of the Inca system (e.g., by a system
administrator).  A reporter should be written using the user-level
monitoring guidelines described in the introduction and could be a simple
Globus~\cite{globus} GRAM gatekeeper ping test (see Figure~\ref{pingReporter})
or a more complex Grid application benchmark~\cite{grasp}.  Reporters must
support certain command line options and produce an XML document or
\emph{report}
according to the Inca reporter schema.  The goal of the reporter schema is to
accommodate multiple types of data and to capture enough information about the
reporter execution to diagnose any detected failures.  The reporter schema
consists of the following elements:

\begin{itemize}
\item a set of header tags describing the context of the reporter
execution:  GMT timestamp, hostname, reporter name, reporter version, working
directory, reporter path, and arguments;
\item an optional set of debug or information log tags similar to log4j~\cite{log4j} output;
\item a body containing the results expressed as any XML sequence; and
\item an exit status tag
indicating whether the reporter was able to complete its test or measurement,
and an optional error message.  
\end{itemize} 
\noindent Because the body of a report can be any XML sequence, it enables
reporters to express a wide variety of information.  Today, we have four
standard body schemas to express software version information, software
functionality or service tests results, usage information, and performance
results.

An extensible set of Perl APIs is provided to handle much of the effort of
writing reporters.  Figure~\ref{pingReporter} shows (a) an Inca reporter that
pings a pre-WS Globus GRAM server and (b) its corresponding output when
executed on a local machine.  The reporter uses two of the Perl APIs:
Inca::Reporter::SimpleUnit and
Inca::Reporter::GridProxy (both subclasses of Inca::Reporter).  The Inca::Reporter API provides convenience
functions for handling the required input arguments
(lines~\ref{pingReporter}(a) 12-14 produces lines \ref{pingReporter}(b)
10-31) and printing the Inca-compliant header and exit status XML tags
(lines~\ref{pingReporter}(a) 3-10, 24 produces \ref{pingReporter}(b)
1-9, 43-46).  It also includes some informational and debug logging functions
similar to log4j.  The log output has been very useful to system
administrators, who can view a summary of the test or benchmark that the
reporter performed without reading the reporter source code.  Line
\ref{pingReporter}(a) 15 shows a special log function, loggedCommand, that
executes a system command (using a 30 second timeout) and logs to the 'system'
level of the log XML output (producing lines \ref{pingReporter}(b) 32-36).  The subclass
Inca::Reporter::SimpleUnit is the API responsible for printing the simplest
standard reporter body schema to report software functionality or service
tests results; it handles the printing of the small body XML
(lines~\ref{pingReporter}(b) 39-41).  Finally, the
Inca::Reporter::GridProxy dependency (line~\ref{pingReporter}(a) 11) adds a proxy
dependency to the reporter, telling the Inca system to download a
short-term proxy before running this reporter (this is discussed further in
Section~\ref{security}).  Most current reporters use the Perl APIs and consist
of fewer than 30 lines of code.

@@

% What are repositories and their key features
Reporter repositories are collections that consist of reporters, required
packages and libraries (including the Perl APIs described in the previous
section), and a catalog file.  Repository contents are usually accessible using a URL
and designed to be shared across multiple Inca deployments.  The catalog file,
patterned after APT's Packages.gz~\cite{apt}, allows the user to indicate
reporter dependencies on CPAN modules, tar.gz packages, and other external
sources.  Inca automatically deploys dependencies into a
subdirectory of its installation (more in Section~\ref{agent}); this enables
reporters to be deployed to resources with minimumal effort.  Each package
specified in the catalog is versioned, allowing Inca to
automatically distribute reporter code updates such as bug fixes.  Because of
this, Inca administrators who maintain repositories need to ensure
that updates to reporters work properly before committing them to a repository.

% We have a lot of reporters ready to be picked 
The Inca team publishes a reporter repository that contains 143 reporters
developed and tested for TeraGrid.  Most reporters are either version
reporters that collect version information from a software package and
serve as a most basic functionality test, unit test reporters that run a more involved
functionality test, or performance benchmark reporters.  The unit and version
reporters cover software such as Grid middleware, compilers, math libraries,
data tools, and visualization tools.  Current performance reporters
measure data transfer and execute Grid benchmarks as described in
Section~\ref{grasp}.

@@

\begin{figure*}[tbp]
  \centering
  \mbox{\epsfig{file=incat.eps, width=\textwidth}}
  \caption{\label{incat_fig} Screenshot of incat that shows the reporters
  and their attributes available from the provided reporter repository.}
\end{figure*}

% Incat is interface Inca admin uses to configure reporters to resources
% introduce series here; why suites are important It is designed to make the
% effort of configuring and maintaining 100s series on resources easilty
The Inca administrative tool (incat) is a GUI implemented in Java Swing that an
Inca administrator uses to configure user-level Grid monitoring on their
resources.  Incat allows an Inca administrator to choose which resources to
monitor and which reporters to deploy to those resources.  The configuration
is stored in a XML file and sent to the agent, which handles the implementation
(as described in the next section).  The Inca administrator can reload the
configuration at any point and make updates.  Incat provides a number of
conveniences that enable a large number of results to be managed and collected
with a minimum effort.

To begin reporter configuration, the Inca administrator enters the location of
one more reporter repositories, and incat loads and displays the reporters
available from them, as shown in Figure~\ref{incat_fig}.
For each reporter, the Inca administrator can specify the resources to run on,
input arguments, the runtime environment, the frequency of execution, resource
limits, and email notifications.  The reports that a reporter produces on a
resource when executed with specific set of input arguments and runtime
environment are known as a \emph{report series} (or \emph{series} for short).
Thus, the grid.globus.gramPing reporter in Figure~\ref{pingReporter} would
produce one report series when executed with host 'tg-login.sdsc.edu' and
another report series when executed with 'dslogin.sdsc.edu'.  A set of related
series can be grouped into \emph{suites} and shared across other Inca
deployments, e.g.,  a Globus suite or a data transfer
performance suite.  Suites can also be useful in determining interoperability
among Grids or whether an application's requirements are being
fulfilled on a Grid.

% Resource information organized to make it easier to maintain
For each monitored resource, an Inca administrator selects an access method
(SSH or Globus) to access the resource and start monitoring there (described
in Sections~\ref{agent} and ~\ref{rm}).  Resources can also be grouped
together and referenced in the series configuration.  This facilitates the
process of executing the same series on multiple resources.  Furthermore,
attributes called \emph{macros} can be attached to resource groups for
reference in series configuration (i.e., inputs
and runtime environment).  For example, it is useful to have a macro called
'jobmanager' since the batch system is likely to differ from one machine to
the next and multiple tests will require its value.  A resource macro can also
have multiple values in which case the series will be executed on the resource
once for each macro value.  The
benefit of resource groups and macros is that when a reporter is executed on a
resource multiple times with different input arguments, it can be represented
succinctly.  Similarly, when a resource attribute is changed it only has to be
changed in one place for every series that references it to be updated.
Inca's initial configuration and maintenance is therefore easier and less error prone.

@@

The Inca agent is a server that implements the configuration specified by the
Inca administrator.  When it receives a configuration file from the Inca
administrator, it will determine which reporters should be executed on each
resource by expanding the resource macros and groups; it then stores the
expanded configuration information in the depot.  The agent stages and
launches an Inca component, called a reporter manager (described in the
following subsection), on each resource using either SSH or Globus.  Once a
reporter manager contacts its agent, the agent transmits the reporters to
execute along with their dependencies and a suite that contains their series
configuration and schedule of execution.  As an Inca administrator makes
updates to the configuration, the agent will push out new reporters and/or
suite changes to each of the affected resources.

To further manage the Inca deployment, the agent regularly pings the reporter
managers on each resource in order to detect when a reporter manager has
failed so it can be restarted.  For example, if a resource goes down for a
planned maintenance, the agent will attempt to restart the reporter manager
(by default every hour) until it succeeds.  The agent also maintains a local
cache of reporters and their dependencies; it periodically checks the
repositories for updates (every 4 hours by default) and automatically
distributes them to the reporter managers if the latest version is desired.  
The agent is implemented in Java.

@@

The Inca reporter manager is a lightweight process responsible for managing
the schedule and execution of Inca reporters on a single resource. The
reporter manager receives reporter updates and dependencies from the agent
along with requests for reporter scheduling changes.  Running under a regular
user account, the reporter manager executes reporters on-demand or using an
internal cron scheduler, and sends reports to the depot for archiving. The
reporter manager monitors reporter system usage using the system command
\texttt{ps} and enforces limits (e.g., wall clock time, CPU time, memory).
System usage information is sent to the depot with each report.

The reporter manager is implemented in Perl since Perl is available by default
on UNIX machines.  The cron scheduling is implemented using the CPAN Perl
module Schedule::Cron.

@@

The Inca depot server is responsible for storing configuration information and
the data produced by reporters. The depot uses a relational database via
Hibernate~\cite{hibernate} so that it can use a variety of databases.  The
depot provides full archiving of reporter output and structures its schema
around series and the minimization of redundant data, i.e., only stores
changes from one report to another in a report series.  The depot also
supports comparisons that are executed on a newly received report; 
% need Jim's help with this sentence
currently regular expression matching and greater than/less than comparisons are 
supported.  Optionally, an Inca administrator can select to receive
email notification when the result of the comparison changes.

Data can be queried using SQL queries. Predefined queries exist to return the
latest report instances of a suite, a single report instance, or a report
history.  A Web services interface is also available to provide
unauthenticated query access to data.  The depot is implemented in Java.

@@

% Should illustrate that we've thought about how Inca can scale
\begin{figure}[tbp]
  \centering
  \includegraphics[width=\columnwidth]{vo.eps}
  \caption{Coordinated Inca Deployments.}
  \label{tg_coord_fig}
\end{figure}

Inca was designed to distribute control and storage workload among
multiple Inca components if needed.  For example, one depot could forward
storage requests and queries to another depot to distribute its workload or to
maintain a mirror for fault tolerance.  Figure~\ref{tg_coord_fig} shows a more
complex scenario where two Inca deployments coordinate with each other.  For
example, application communities like GEON have their own Grid but also have
access to resources on TeraGrid.   Two separate Inca deployments can result in
duplicate testing. Instead, one Inca deployment can coordinate the execution
of a suite with another deployment.
Figure~\ref{tg_coord_fig} shows this type of coordinated deployment, where Grid B 
has its own resources but also has access to resources in Grid A.
When an Inca administrator submits a suite to Grid B, the Inca agent running
on Grid B will determine which reporters run on Grid A resources and forward
them as a suite request to Grid A's agent.  If Grid B has permission to submit
suites, Grid A's agent will execute the suite and configure its depot to
forwards results back to Grid B's depot.

@@

% Description and Requirements - Describe CTSS
Requirements for user-level Grid monitoring on TeraGrid initially included the
validation and verification of CTSS on each resource.  As described in the
introduction, CTSS was designed to
allow users to more easily run Grid jobs across its distributed, heterogeneous
resources.  CTSS version 3 (CTSSv3) is available from all TeraGrid compute
resources and contains approximately 30 software packages that provide
Grid tools and services (e.g., Globus, GSI-SSH, MyProxy), data management
tools (e.g., SRB, HDF5), and applications tools (e.g., MPICH, GCC).

>>>>

% Standard "Grids are good" intro paragraph.  But are complex.  
Grid systems provide unified and coherent access to distributed computing,
data storage and analysis, instruments, and other resources.  These systems
require the careful coordination of software packages, services, and
configurations across multiple, potentially heterogeneous, resources.  The TeraGrid
project~\cite{teragrid}, for example, manages the coordination of software and
services by deploying and monitoring a common user environment across
distributed, heterogeneous resources. 
TeraGrid's software and services uniformity simplifies access to its
resources, which consist of more than 102 teraflops of compute capability and
more than 15 petabytes of online storage, all interconnected by a network that
can transfer a terabyte of data in under 10 minutes.

% Complex means they are difficult to provide and maintain. Describe the
% stakeholders.   Monitoring is needed.
Providing and maintaining a stable infrastructure for these complex 
Grid systems poses challenges for both administrators who build and
maintain Grid resources and scientists who use them.  System
administration is distributed across multiple administrative domains 
requiring a significant amount of coordination.  This is typically performed by
a group of Grid administrators or operators who consider local site policies and
resource heterogeneity
and decide when software (including updates and patches) should be deployed to
resources and how it should be configured.  
Each site's system administrators, who are not necessarily Grid
experts, are then responsible for providing the required Grid software
components and services for their resource and debugging any problems that
arise.  Well-defined requirements and good communication are required in this
model.  Otherwise, inconsistencies arise between the resources that either
inconvenience the user or prevent them from using a particular resource
altogether.  A second challenge is that failures will occur over
time in the Grid services due to network or system failures, software
misconfiguration, or software bugs. 
Grid monitoring can be used to detect such problems, leading to a more
stable and dependable Grid infrastructure.

@@

% What user-level monitoring provides and why we think it is good
User-level Grid monitoring provides Grid infrastructure testing and performance measurement 
from a generic, impartial user's perspective.  The goal of user-level monitoring is 
to detect and fix Grid infrastructure problems before users notice them -- 
user complaints should not be the first indication of Grid failures.  
In our view, the following are features of user-level Grid monitoring:

@@

\item Runs from a standard user
account in order to reflect regular user experiences.  It is important not to execute from a system administrator's account,
because it may have special privileges and use custom shell initialization files.

\item Executes with a standard user GSI
credential, which is mapped to the standard user account, when tests or performance measurements require authentication to Grid services.

\item Emulates a regular user using tests and performance
measurements that are written and configured using information directly from user documentation
(e.g., hostnames, ports, pathnames, etc.). 
This may not always be possible
when documentation and testing are done in parallel in a pre-production
environment, but they should be closely coordinated activities.

\item Centrally manages the configuration of user-level tests or performance measurements in order to ensure consistent testing of the resources, rather than
by system administrators who may not use the same information that is
available to users.

\item Is easy to update
and maintain as user-level tests and performance measurements often need
to be updated when the Grid infrastructure is upgraded.
It is also difficult to write and deploy a test correctly the first time
because of portability issues and incomplete user documentation.  Multiple
iterations are usually required to determine whether a detected failure stems
from a faulty test, user documentation, or Grid resource.

\item Provides a representative indication of Grid status by testing
documented user commands and individual Grid software components.

\item Automates the execution of user-level tests or performance measurements
periodically since Grids are dynamic.

\item Executes locally on all Grid
resources when appropriate so that all Grid access points available to users
are verified.  Similarly, it is important to execute some tests all-to-all
in order to detect site-to-site configuration errors such as authentication
problems.

@@

\noindent In 2003 SDSC, in partnership with TeraGrid, began developing Inca
1~\cite{inca1} to implement a user-level Grid monitoring system that provided
these features.  At that time, the only available user-level Grid
monitoring tools were the NCSA TestGrid script~\cite{ncsa-test} and
Grid Integration Test Script (GITS)~\cite{gits}, both of which ran a fixed number of Grid tests and formatted
results in HTML.  Although these tools were easy to install and produced
useful information, they showed the view of the Grid from a single
resource, lacked automation, and were not easily extensible.  Inca 1 provided
the means to verify the common user environment was deployed consistently across all TeraGrid
resources and monitored its status.

The initial
version of Inca was implemented as a client-server architecture.  It provided
data collection, data storage (accessible from a Web services interface and with 
limited archiving capabilities), and data display though Web status
pages.  Inca 1 was first deployed to TeraGrid in mid 2003 and released in late
2003. Running Inca 1 for a year and a half on TeraGrid taught 
valuable lessons that have been incorporated into the design of Inca 2, our
current release.  Inca 2
contains a number of substantial improvements over Inca 1 with respect to
security, installation and maintenance, and storage capabilities.  Inca 2 has
been running on TeraGrid since November 2006 and a production
version of the software was released in February 2007.  Currently, seven other Grids in the
U.S., Europe, and Australia use Inca 2.

@@

\begin{figure*}[tbp]
  \centering
  \includegraphics[width=.6\textwidth]{arch.eps}
  \caption{\label{arch_fig} Inca architecture.}
\end{figure*}

% Implements user-level Grid monitoring and who it benefits
Inca 2 is a system that provides user-level monitoring of Grid functionality
and performance.  It was designed to be
general, flexible, scalable, and secure, in addition to being easy to deploy
and maintain.  Inca benefits Grid operators who oversee the day-to-day
operation of a Grid; system administrators who provide and manage resources;
and users who run applications on a Grid.  Besides implementing the features
described in Section~\ref{intro}, Inca 2 has additional features
listed below.  A '*' after the feature description indicates it is a new
feature of Inca 2; other items note improvements to Inca 1 features.  The 
Inca system:

@@

% overview description of components
Figure~\ref{arch_fig} shows the architecture of Inca 2.
Inca 2 incorporates three core
components (highlighted box):  the agent, depot, and reporter manager.
The \textit{agent} and \textit{reporter managers} coordinate the execution of
tests and performance measurements on the Grid resources and the
\textit{depot} stores and archives the results.  The inputs to Inca 2 are one
or more \textit{reporter repositories} that contain user-level tests and
benchmarks, called \textit{reporters}, and a configuration file describing how
to execute them on the Grid resources.  This configuration is normally created
using an administration GUI tool
called \textit{incat} (Inca Administration Tool).  The output or results
collected from the resources are queried by the \textit{data consumer} and
displayed to users.  The following steps describe how an Inca administrator
would deploy user-level tests and/or performance measurements to their
resources.

@@

\item The Inca
administrator either writes reporters to monitor the user-level functionality
and performance of their Grid or uses existing
reporters in a published repository.

@@

An Inca reporter is an executable program that tests or measures some aspect
of a system or installed software.   Reporter executables are designed to be
easy to produce and can be run outside of the Inca system (e.g., by a system
administrator).  Existing reporters range from a simple Globus~\cite{globus}
GRAM gatekeeper ping test (see Figure~\ref{pingReporter})
to complex Grid application benchmarks~\cite{grasp}.  Reporters must
support certain command line options and produce an XML document, or
\emph{report},
according to the Inca reporter schema.  The goal of the reporter schema is to
accommodate multiple types of data and to capture enough information about the
reporter execution to diagnose any detected failures.  The reporter schema
consists of the following elements:

\begin{itemize}
\item a set of header tags describing the context of the reporter
execution:  GMT timestamp, hostname, reporter name, reporter version, working
directory, reporter path, and arguments;
\item an optional set of debug or information log tags similar to log4j~\cite{log4j} output;
\item a body containing the results expressed as an XML sequence; and
\item an exit status tag
indicating whether the reporter was able to complete its test or measurement,
and an optional error message.  
\end{itemize} 
\noindent Because the body of a report can be any XML sequence, it enables
reporters to express a wide variety of information.  Today, we have four
standard body schemas to express software version information, software
functionality or service tests results, usage information, and performance
results.

An extensible set of Perl APIs is provided to handle much of the effort of
writing reporters.  Figure~\ref{pingReporter} shows (a) an Inca reporter that
pings a pre-WS Globus GRAM server and (b) its corresponding output when
executed on a local machine.  The reporter uses two of the Perl APIs:
Inca::Reporter::SimpleUnit (a subclass of Inca::Reporter) and
Inca::Reporter::GridProxy.  The Inca::Reporter API provides convenience
functions for handling the required input arguments
(lines~\ref{pingReporter}(a) 12-14 produces lines \ref{pingReporter}(b)
10-31) and printing the Inca-compliant header and exit status XML tags
(lines~\ref{pingReporter}(a) 3-10, 24 produces \ref{pingReporter}(b)
1-9, 43-46).  It also includes some informational and debug logging functions
similar to log4j.  The log output has been very useful to system
administrators, who can view a summary of the test or benchmark that the
reporter performed without reading the reporter source code.  Line
\ref{pingReporter}(a) 15 shows a special log function, loggedCommand, that
executes a system command (using a 30 second timeout) after logging it to the
'system' level of the log XML (producing lines \ref{pingReporter}(b) 32-36).  The subclass
Inca::Reporter::SimpleUnit is the API responsible for printing the simplest
standard reporter body schema to report software functionality or service
tests results; it handles the printing of the small body XML
(lines~\ref{pingReporter}(b) 39-41).  Finally, the
Inca::Reporter::GridProxy dependency (line~\ref{pingReporter}(a) 11) adds a proxy
dependency to the reporter, telling Inca to download a
short-term proxy before running this reporter (as discussed in
Section~\ref{security}).  Most current reporters use the Perl APIs and consist
of fewer than 30 lines of code.

@@

% What are repositories and their key features
Reporter repositories are collections that consist of reporters, required
packages and libraries (including the Perl APIs described in the previous
section), and a catalog file.  Repository contents are accessible using a URL
and designed to be shared across multiple Inca deployments.  The catalog file,
patterned after APT's Packages.gz~\cite{apt}, allows the user to indicate
reporter dependencies on CPAN modules, tar.gz packages, and other external
sources.  Inca automatically deploys dependencies into a
subdirectory of its installation (more in Section~\ref{agent}); this enables
reporters to be deployed to resources with minimal delay.  Each package
specified in the catalog is versioned, allowing Inca to
automatically distribute reporter code updates such as bug fixes.  Because of
this, Inca administrators who maintain repositories need to ensure
that updates to reporters work properly before committing them to a repository.

% We have a lot of reporters ready to be picked 
The Inca team publishes a reporter repository that contains 143 reporters
developed and tested for TeraGrid.  Most reporters are either version
reporters that collect version information from a software package,
unit test reporters that run a more involved
functionality test, or performance benchmark reporters.  The unit and version
reporters cover software such as Grid middleware, compilers, math libraries,
data tools, and visualization tools.  Current performance reporters
measure data transfer and execute Grid benchmarks as described in
Section~\ref{grasp}.

@@

\begin{figure*}[tbp]
  \centering
  \mbox{\epsfig{file=incat.eps, width=.9\textwidth}}
  \caption{\label{incat_fig} Screenshot of incat that shows the reporters
  and their attributes available from the provided reporter repository.}
\end{figure*}

% Incat is interface Inca admin uses to configure reporters to resources
% introduce series here; why suites are important It is designed to make the
% effort of configuring and maintaining 100s series on resources easilty
The Inca administrative tool (incat) is a Java Swing GUI that an
Inca administrator uses to configure user-level Grid monitoring on their
resources.  Incat allows an Inca administrator to choose which resources to
monitor and which reporters to deploy to those resources.  The configuration
is stored in a XML file and sent to the agent, which handles the implementation
(as described in the next section).  The Inca administrator can reload the
configuration at any point and make updates.  Incat provides a number of
conveniences that enable a large number of results to be managed and collected
with a minimum effort.

To begin reporter configuration, the Inca administrator enters the location of
one more reporter repositories, and incat loads and displays the reporters
available from them (Figure~\ref{incat_fig}).
For each reporter, the Inca administrator can specify the resources to run on,
input arguments, the runtime environment, the frequency of execution, resource
limits, and email notifications.  The reports that a reporter produces on a
resource when executed with specific set of input arguments and runtime
environment are known as a \emph{report series} (or \emph{series} for short).
Thus, the grid.globus.gramPing reporter in Figure~\ref{pingReporter} would
produce one report series when executed with 'blue.ufo.edu' as the host argument and another report series with 'red.ufo.edu'.  A set of related
series can be grouped into \emph{suites} and shared across other Inca
deployments, e.g.,  a Globus suite or a data transfer
performance suite.  Suites can also be useful in determining interoperability
among Grids or whether an application's requirements are being
fulfilled on a Grid.

% Resource information organized to make it easier to maintain
For each monitored resource, an Inca administrator selects an access method
(SSH or Globus) to access the resource and start monitoring there (described
in Sections~\ref{agent} and ~\ref{rm}).  Resources can be aggregated into
groups for reference in the series configuration, facilitating the
process of executing the same series on multiple resources.  Also,
input and runtime environment attributes can be attached to resource groups
for reference in series configuration.
These resource \emph{macros} can have multiple values, in which
case the series will be executed on the resource once for each macro value.
Resource groups and macros ease the process of defining and maintaining
multiple similar series.

@@

The Inca agent is a server that implements the configuration specified by the
Inca administrator.  When the agent receives a configuration from incat,
it expands any resource group and macro references to determine
the series to execute on each resource and stores this
information in the depot.  The agent stages and
launches an Inca component, called a reporter manager (described in the
following subsection), on each resource, using either SSH or Globus.  After a
reporter manager contacts its agent, the agent transmits the reporters to
execute, any dependencies, and a suite that contains series
configuration and an execution schedule.  As an Inca administrator makes
updates to the configuration, the agent will push out new reporters and/or
suite changes to each of the affected resources.

The agent regularly pings its reporter managers in order to detect when one has
failed (for example, when a system is taken down for maintenance) and so must
be restarted.  The agent also maintains a local cache of reporters and their
dependencies; it periodically checks repositories (every 4 hours by default)
and automatically distributes reporter updates to the reporter managers as
needed.  The agent is implemented using Java.

@@

The Inca reporter manager is a lightweight process responsible for managing
the schedule and execution of Inca reporters on a single resource. The
reporter manager receives reporter updates and dependencies from the agent
along with requests for reporter scheduling changes.  Running under a regular
user account, the reporter manager executes reporters on-demand or using an
internal cron scheduler and sends reports to the depot for archiving. The
reporter manager monitors reporter system usage 
and enforces limits (e.g., wall clock time, CPU time, memory).
System usage information is sent to the depot with each report. 
The reporter manager is implemented using Perl to make it easy to install on
a wide variety of UNIX systems.

@@

The Inca depot server is responsible for storing configuration information and
the data produced by reporters. The depot uses a relational database via
Hibernate~\cite{hibernate}, enabling the use of a variety of database backends.
The depot provides full archiving of reporter output, and the database schema is
tuned to minimize redundant data.  Inca administrators can specify comparison
tests to run on reports as they are received, and the depot will send email
when the results of these comparisons change.  This provides the administrator
with quick notification of problems as they appear and of the results of
repairs.

Data can be queried using SQL queries. Predefined queries exist to return the
latest report instances of a suite, a single report instance, or a report
history.  A Web services interface is also available to provide
unauthenticated query access to data.  The depot is implemented using Java.

@@

% Should illustrate that we've thought about how Inca can scale
\begin{figure*}[tbp]
  \centering
  \includegraphics[width=.6\textwidth]{vo.eps}
  \caption{\label{tg_coord_fig} Coordinated Inca deployments.}
\end{figure*}

Inca was designed to distribute control and storage workload among
multiple Inca components if needed.  For example, one depot could forward
storage requests and queries to another depot to distribute its workload or to
maintain a mirror for fault tolerance.  Figure~\ref{tg_coord_fig} shows a more
complex scenario where two Inca deployments coordinate with each other.  For
example, application communities like GEON have their own Grid but also have
access to resources on TeraGrid.   Two separate Inca deployments can result in
duplicate testing. Instead, one Inca deployment can coordinate the execution
of a suite with another deployment.
Figure~\ref{tg_coord_fig} shows this type of coordinated deployment, where Grid B 
has its own resources but also has access to resources in Grid A.
When an Inca administrator submits a suite to Grid B, the Inca agent running
on Grid B will determine which reporters run on Grid A resources and forward
them as a suite request to Grid A's agent.  If Grid B has permission to submit
suites, Grid A's agent will execute the suite and configure its depot to
forwards results back to Grid B's depot.  Forwarding is not yet implemented 
in Inca 2.

@@

%\begin{figure}[tbp]
%  \centering
%  \includegraphics[width=.8\columnwidth]{tg-deploy.eps}
%  \caption{\label{tg_deploy_fig} TeraGrid's Inca 2 Deployment.}
%\end{figure}
%\begin{figure}[tbp]
%  \centering
%  \includegraphics[width=.4\textwidth]{status-page.eps}
%  \caption{\label{status_page_fig} Portion of the TeraGrid CTSSv3 detailed status page with the resources anonymized.}
%\end{figure}

\begin{figure*}[tbp]
\subfigure[]{\includegraphics[width=.8\columnwidth]{tg-deploy.eps}}
\subfigure[]{\includegraphics[width=.6\textwidth]{status-page.eps}}
  \caption{\label{tg_deploy_fig}\label{status_page_fig} (a) TeraGrid's Inca 2
  deployment and (b) portion of the TeraGrid CTSSv3 detailed status page with
  the resources anonymized.}
\end{figure*}

% Description and Requirements - Describe CTSS
Requirements for user-level Grid monitoring on TeraGrid initially included the
validation and verification of Coordinated TeraGrid Software and Services (CTSS) 
on each TeraGrid resource.  As described in the introduction, CTSS was designed to
allow users to more easily run Grid jobs across its distributed, heterogeneous
resources.  CTSS version 3 (CTSSv3) is available from all TeraGrid compute
resources and contains approximately 30 software packages that provide
Grid tools and services (e.g., Globus, GSI-SSH, MyProxy), data management
tools (e.g., SRB, HDF5), and applications tools (e.g., MPICH, GCC).
